--
title: "Week 2 data check template: PHW253 Descriptive Epidemiology Assignment"
author: "student"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
# Show R code in output for all R chunks
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

# * Purpose: Code for Week 2 data check of the Descriptive Epi Assignment
# * Data: PH W253 Descriptive Epi Assignment line list_redacted.xlsx

##### Step 1: Copy all of the code needed to complete the Week 1 data check including: 
##### library code for all packages listed in Week 1 template,
##### importing the dataset, 
##### and creating new dataset and keep only rows where MLVA is an A, A2,A3 pattern






#### Step 2: Look at State variable
```{r}

```

#### Step 3: Define region using census definition  https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf
```{r}

```



#### Step 4: Look at region variable and tabulate number of cases by region

```{r}

```


#### Step 5: Dates in R: What format is OnsetDate in?
```{r}

```


##### Step 6: Create a new variable with onset date in ymd date format and confirm new variable format
```{r}

```


##### Step 7: Can tabulate new variable to obtain date ranges and determine if there are missing values
```{r}

```

