---
title: "Week 4 Data Check Template"
author: "student"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
# Show R code in output for all R chunks
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

* Purpose: Code for Week 4 data check of the Hypothesis Testing Assignment
* Data: PHW253_Wk6_CaseControlStudy_redacted_notxt.xlsx


# Preliminary

Call in the necessary R packages for this assignment.

## install packages 
## (just run once and then comment out by adding ## in front of line)
## install.packages("rio")
## install.packages("skimr")
## install.packages("dplyr")
## install.packages("janitor")
## install.packages("survival")

 
###### Step 0: Load packages
 
```{r}
## load packages
## run everytime

## rio needed for import code
library(rio)
## dplyr needed for mutate or recode
library(dplyr)
## janitor needed for crosstable
library(janitor)
## survival needed for clogit
library(survival)
```

# Data Set

##### Step 1: Import the data. Look at the variable names and use janitor package to clean variable names.

## In Weeks 1-3, we used line listing (a dataset with only the cases)
## In Weeks 4-6, we will use outbreak investigation dataset (a matched case-control study)
```{r}
## import


## look at the dataset 
## example: names(dataset)


## janitor package clean names changes the column names to lower case & replaces
## the spaces in column names with an underscore
## example: newnamedataset<- dataset  %>% janitor::clean_names()



```

##### Step 2: Subset the data (all code is provided)

The data set contains more records than needed for the matched case-control study. Thus, you will have to subset the data in order to get the study data set.

```{r}
## Select only cases that have matched controls
ecoli2 <- ecoli1 %>% 
  filter(cdcid !="CDC001" & cdcid !="CDC006" & cdcid !="CDC009" & cdcid !="CDC012" & 
           cdcid !="CDC015" & cdcid !="CDC022" & cdcid !="CDC023" & cdcid !="CDC024" & 
           cdcid !="CDC037" & cdcid !="CDC043" & cdcid !="CDC045" & cdcid !="CDC046" & 
           cdcid !="CDC048" & cdcid !="CDC049" & cdcid !="CDC067" & cdcid !="CDC068")   

## Some cases have multiple controls
ecoli2 %>%  filter(cdcid == "CDC047")  %>% tabyl(case)

## Only keep controlletter=A for cdcid=="CDC047"
x<-which(ecoli2$cdcid =="CDC047" & ecoli2$controlletter=="B")   
ecoli3 <-ecoli2[-x, ]    

dim(ecoli3)
```

##### Step 3: Tabulate number of total cases and total controls in cleaned dataset 
## In Week 6, these are the numbers you'll add to the column headings in the provide table template 

```{r}



```


##### Step 4: Look at the strawberry variable. For conditional logistic regression, all values need to be 0 or 1. 
##### Recode other values to missing. 

```{r}

```



##### Step 4: Tabulate the count of cases who ate strawberries. Tabulate the count of controls who ate strawberries. 
```{r}



```



##### Step 5: Calculate the percent exposed among all cases. Calculate the percent exposed among all controls.
```{r}

```






 




 



