---
title: "Week 5 Data Check Template"
author: "Wayne Enanoria"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
# Show R code in output for all R chunks
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

* Purpose: Code for Week 5 Data Check Template 
* Data: PHW253_Wk6_CaseControlStudy_redacted_notxt.xlsx


# Preliminary

Call in the necessary R packages for this assignment.

## install packages 
## (just run once and then comment out by adding ## in front of line)
## install.packages("rio")
## install.packages("skimr")
## install.packages("dplyr")
## install.packages("janitor")
## install.packages("survival")

 
###### Step 0: Load packages. Import dataset. Subset the data (all code is provided in Week 4). 
###### For conditional logistic regression, all food item values need to be 0 or 1; recode other values to missing. 
 
```{r}

```

###### Step 1: Need to create a numeric variable that identifies each pair (all code is provided)

## this is called strata in the regression code
## first, select last two characters of the CDCID string/character variable (new variable stratachar)
## then, convert to a numeric format (new variable stratanum)

```{r}
ecoli3$stratachar<-substr(ecoli3$cdcid,start=5,stop=6)

ecoli3 %>%  tabyl(stratachar)

ecoli3$stratanum<-as.numeric(ecoli3$stratachar)

ecoli3 %>%  tabyl(stratachar,stratanum)
```



 
##### Step 2: Conidtional logsitic regression.
 
```{r}
## See Week5 Conditional Logistic Regression lecture video and code on datahub for example code



```





 



