--
title: "Week 1 data check template: PHW253 Descriptive Epidemiology Assignment"
author: "student"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
# Show R code in output for all R chunks
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

# * Purpose: Code for Week 1 data check of the Descriptive Epi Assignment
# * Data: PH W253 Descriptive Epi Assignment line list_redacted.xlsx


# Preliminary

#  You may have to install new packages for this assignment. 

## install packages 
## (just run once and then comment out by adding ## in front of line)
## install.packages("rio")
## install.packages("dplyr")
## install.packages("janitor")
## install.packages("flextable")
## install.packages("lubridate")
## install.packages("incidence2")
## install.packages("ggplot2")

```{r}
## load packages
## run everytime
## rio needed for import code
library("rio")

## dplyr needed for mutate or recode
library(dplyr)

## janitor needed for crosstable
library(janitor)

## flextable needed for export formatted table to Word file
library(flextable)

# for dates in R
library(lubridate)

# ggplot2 for epicurves & data visualization
library (ggplot2)

# incidence2 for epicurves of linelist data
library (incidence2)
```

# Data Set

##### Step 1: Import in the data. And look at the structure of the dataset.

##### ADD CODE HERE


# Assignment


# Descriptive Epi Assignment instructions  
# state "same outbreak MLVA pattern (Pattern A, A2, and A3)"

# there are 92 observations in the data set
# 75 cases had are MLVA pattern A, 1 case pattern A2, 1 case pattern A3
# other E.coli cases did not have MLVA pattern A, A2, or A3 and are not a part of this outbreak

#### Step 2: create new dataset and keep only rows where MLVA is an A, A2,A3 pattern

##### ADD CODE HERE


#### Step 3: Look at hospital variable and tabulate number of hospitalizations "Yes" "No" and "Unknown"

##### ADD CODE HERE
